Streaming CityJSON datasets

### 2024-04-24 paper/main.tex
Update size of datasets + shared vertices

\begin{table*}
  \centering
  \begin{threeparttable}
  \caption{The datasets used for the benchmark. }%
  \label{tab:datasets}
  \small
  \begin{tabular}
    {@{}lcccccrrrcrr@{}}\toprule
    &&  \multicolumn{3}{c}{\textbf{dataset}} && \multicolumn{3}{c}{\textbf{size of file}} && \multicolumn{2}{c}{\textbf{vertices}}   \\ 
    \cmidrule{3-5} \cmidrule{7-9} \cmidrule{11-12} 
     && CityObjects &  LoDs & appearance\footnotesize ${}^{\text{(a)}}$ && CityJSON & CityJSONSeq & compr.\footnotesize ${}^{\text{(b)}}$ && total & largest\footnotesize ${}^{\text{(c)}}$ \\
    \midrule
    \textbf{3DBAG}          && \qty{1110} bldgs & 0+1.2+1.3+2.2 & &&    \qty{6.7}{\mega\byte} & \qty{4.3}{\mega\byte} &  64\%  &&   \num{82509} &  \num{4112} \\
    \textbf{Helsinki}       && \qty{77231} bldgs   & 1+2   &         && \qty{600}{\mega\byte} & \qty{432}{\mega\byte} &  72\%  && \num{3038576} &  \num{2202} \\
    \textbf{Helsinki\_tex}  && \qty{77231} bldgs   & 1+2   & tex     && \qty{748}{\mega\byte} & \qty{675}{\mega\byte} &  90\%  && \num{3038576} &  \num{2202} \\
    \textbf{Ingolstadt}     && \qty{55} bldgs      & 3     &         && \qty{5.1}{\mega\byte} & \qty{4.0}{\mega\byte} &  78\%  &&   \num{87972} & \num{12800} \\
    \textbf{Montréal}       && \qty{294} bldgs     & 2     & tex     && \qty{5.4}{\mega\byte} & \qty{4.6}{\mega\byte} &  85\%  &&   \num{31585} &  \num{3393} \\
    \textbf{NYC}            && \qty{23777} bldgs   & 2     &         && \qty{105}{\mega\byte} &  \qty{95}{\mega\byte} &  90\%  && \num{1035804} &  \num{2608} \\
    \textbf{Railway}        && \qty{50} diff       & 3     & tex+mat && \qty{4.5}{\mega\byte} & \qty{4.2}{\mega\byte} &  93\%  &&   \num{73554} & \num{14966} \\
    \textbf{Rotterdam}      && \qty{853} bldgs     & 2     & tex     && \qty{2.6}{\mega\byte} & \qty{2.7}{\mega\byte} & 104\%  &&   \num{22246} &   \num{631} \\
    \textbf{Vienna}         && \qty{307} bldgs     & 2     &         && \qty{5.4}{\mega\byte} & \qty{4.8}{\mega\byte} &  89\%  &&   \num{47220} &  \num{2025} \\
    \textbf{Zürich}         && \qty{52834} bldgs   & 2     &         && \qty{279}{\mega\byte} & \qty{247}{\mega\byte} &  89\%  && \num{3472989} &  \num{4069} \\
    \bottomrule
  \end{tabular}
    \begin{tablenotes}[flushleft]
      \footnotesize
      \item ${}^{\text{(a)}}$ `tex' is textures stored; `mat' is material stored
      \item ${}^{\text{(b)}}$ compression is $\frac{CityJSONSeq}{CityJSON}$, smaller is better
      \item ${}^{\text{(c)}}$ number of vertices in the largest feature of the stream
    \end{tablenotes}
  \end{threeparttable}
\end{table*}

>>>>

\begin{table*}
  \centering
  \begin{threeparttable}
  \caption{The datasets used for the benchmark. }%
  \label{tab:datasets}
  \small
  \begin{tabular}
    {@{}lcccccrrrcrrr@{}}\toprule
    &&  \multicolumn{2}{c}{\textbf{dataset}} && \multicolumn{3}{c}{\textbf{size of file}} && \multicolumn{3}{c}{\textbf{vertices}}   \\ 
    \cmidrule{3-4} \cmidrule{6-8} \cmidrule{10-12} 
     && CityObjects &  app.\footnotesize ${}^{\text{(a)}}$ && CityJSON & CityJSONSeq & compr.\footnotesize ${}^{\text{(b)}}$ && total & largest\footnotesize ${}^{\text{(c)}}$ & shared \\
    \midrule
    \textbf{3DBAG}          && \qty{1110} bldgs    &         && \qty{6.7}{\mega\byte} & \qty{5.9}{\mega\byte} &  88\%  &&     \num{82509} &    \num{4112} &  0.1\% \\
    \textbf{3DBV}           && \qty{71634} diff    &         && \qty{378}{\mega\byte} & \qty{317}{\mega\byte} &  84\%  &&   \num{4110319} &  \num{116670} & 21.0\% \\
    \textbf{Helsinki}       && \qty{77231} bldgs   &         && \qty{572}{\mega\byte} & \qty{412}{\mega\byte} &  72\%  &&   \num{3038576} &    \num{2202} &  0.0\% \\
    \textbf{Helsinki\_tex}  && \qty{77231} bldgs   & tex     && \qty{713}{\mega\byte} & \qty{644}{\mega\byte} &  90\%  &&   \num{3038576} &    \num{2202} &  0.0\% \\
    \textbf{Ingolstadt}     && \qty{55} bldgs      &         && \qty{4.8}{\mega\byte} & \qty{3.8}{\mega\byte} &  79\%  &&     \num{87972} &   \num{12800} &  0.0\% \\
    \textbf{Montréal}       && \qty{294} bldgs     & tex     && \qty{5.4}{\mega\byte} & \qty{4.6}{\mega\byte} &  85\%  &&     \num{31585} &    \num{3393} &  2.0\% \\
    \textbf{NYC}            && \qty{23777} bldgs   &         && \qty{105}{\mega\byte} &  \qty{95}{\mega\byte} &  90\%  &&   \num{1035804} &    \num{2608} &  0.8\% \\
    \textbf{Railway}        && \qty{50} diff       & tex+mat && \qty{4.3}{\mega\byte} & \qty{4.0}{\mega\byte} &  93\%  &&     \num{73554} &   \num{14966} &  0.4\% \\
    \textbf{Rotterdam}      && \qty{853} bldgs     & tex     && \qty{2.6}{\mega\byte} & \qty{2.7}{\mega\byte} & 104\%  &&     \num{22246} &     \num{631} & 20.0\% \\
    \textbf{Vienna}         && \qty{307} bldgs     &         && \qty{5.4}{\mega\byte} & \qty{4.8}{\mega\byte} &  89\%  &&     \num{47220} &    \num{2025} &  0.0\% \\
    \textbf{Zürich}         && \qty{52834} bldgs   &         && \qty{279}{\mega\byte} & \qty{247}{\mega\byte} &  89\%  &&   \num{3472989} &    \num{4069} &  2.6\% \\
    \bottomrule
  \end{tabular}
    \begin{tablenotes}[flushleft]
      \footnotesize
      \item ${}^{\text{(a)}}$ appearance: `tex' is textures stored; `mat' is material stored
      \item ${}^{\text{(b)}}$ compression is $\frac{CityJSONSeq}{CityJSON}$, smaller is better
      \item ${}^{\text{(c)}}$ number of vertices in the largest feature of the stream
    \end{tablenotes}
  \end{threeparttable}
\end{table*}
